Normalization by Evaluation for Sized Dependent Types

### 2017-02-27 nbe/icfp17.tex
[ ICFP 17 ] Fixed typo in abstract

In this article, we integrate dependent types and sized types with higher-rank size polymorphism, which is essential for generic programming and abstraction.  We introduce a size quantifier $\forall$ which lets us ignore sizes in terms for equality checking, alongside with a second quantifier $\Pi$ for abstracting over sizes that do affect the semantics of types and terms.  Judgmental equality is decided by an adaption of normalization-by-evaluation for our new type theory, which features \emph{type shape}-directed reflection and reification.  It follows that subtyping and type checking of normal forms are decidable as well, the latter by a bidirectional algorithm.
\end{abstract}

>>>>

In this article, we integrate dependent types and sized types with higher-rank size polymorphism, which is essential for generic programming and abstraction.  We introduce a size quantifier $\forall$ which lets us ignore sizes in terms for equality checking, alongside with a second quantifier $\Pi$ for abstracting over sizes that do affect the semantics of types and terms.  Judgmental equality is decided by an adaptation of normalization-by-evaluation for our new type theory, which features \emph{type shape}-directed reflection and reification.  It follows that subtyping and type checking of normal forms are decidable as well, the latter by a bidirectional algorithm.
\end{abstract}
